Supporting Information

### 2018-02-27 SupportingInformation.Rmd
added both kendall and spearman preserving surrogte runs to the nonparametric tests of tail dependence for soil C and N data

#get surrogates and get stats for them
cop<-normalCopula(.5,2)
numsurrog<-1000
surv<-copsurrog2d(v,cop,numsurrog)
statsurr<-matrix(NA,length(stat),numsurrog)
rownames(statsurr)<-names(stat)
for (counter in 1:dim(surv)[3])
{
  h<-copsync(surv[,,counter])
  h<-unlist(h[c(2:5,7,8,10:13)])
  h<-c(h[1:4],h[3]-h[4],h[5:6],h[5]-h[6],h[7:8],h[7]-h[8],h[9:10],h[9]-h[10])
  statsurr[,counter]<-unname(h)
}

#now get fractions of surrogates lt the data and gt the data for each stat
stattab<-data.frame(statname=names(stat),stat=unname(stat),frac_surr_gt=NA,frac_surr_lt=NA)
for (counter in 1:length(stat))
{
  stattab[counter,3]<-sum(statsurr[counter,]>stat[counter])/numsurrog
  stattab[counter,4]<-sum(statsurr[counter,]<stat[counter])/numsurrog
}
```

<!--Display the table generated above-->
```{r table_stat_soilCN, echo=F, results="asis"}
table_nums("table_stat_soilCN",display=F)
knitr::kable(data.frame(stat=stattab),caption = "Results of non-parametric tests of tail dependence and asymmetry of tail dependence for the soil C and N dataset.")
```

>>>>

#get surrogates and get stats for them, preserving kendall
cop<-normalCopula(.5,2)
numsurrog<-1000
surv<-copsurrog2d(v,cop,"kendall",numsurrog)
statsurr_k<-matrix(NA,length(stat),numsurrog)
rownames(statsurr_k)<-names(stat)
for (counter in 1:dim(surv)[3])
{
  h<-copsync(surv[,,counter])
  h<-unlist(h[c(2:5,7,8,10:13)])
  h<-c(h[1:4],h[3]-h[4],h[5:6],h[5]-h[6],h[7:8],h[7]-h[8],h[9:10],h[9]-h[10])
  statsurr_k[,counter]<-unname(h)
}

#same, preserving spearman
surv<-copsurrog2d(v,cop,"spearman",numsurrog)
statsurr_s<-matrix(NA,length(stat),numsurrog)
rownames(statsurr_s)<-names(stat)
for (counter in 1:dim(surv)[3])
{
  h<-copsync(surv[,,counter])
  h<-unlist(h[c(2:5,7,8,10:13)])
  h<-c(h[1:4],h[3]-h[4],h[5:6],h[5]-h[6],h[7:8],h[7]-h[8],h[9:10],h[9]-h[10])
  statsurr_s[,counter]<-unname(h)
}

#now get fractions of surrogates lt the data and gt the data for each stat
stattab<-data.frame(statname=names(stat),stat=unname(stat),frac_surr_gt_k=NA,frac_surr_lt_k=NA,frac_surr_gt_s=NA,frac_surr_lt_s=NA)
for (counter in 1:length(stat))
{
  stattab[counter,3]<-sum(statsurr_k[counter,]>stat[counter])/numsurrog
  stattab[counter,4]<-sum(statsurr_k[counter,]<stat[counter])/numsurrog
  stattab[counter,5]<-sum(statsurr_s[counter,]>stat[counter])/numsurrog
  stattab[counter,6]<-sum(statsurr_s[counter,]<stat[counter])/numsurrog
}
```

<!--Display the table generated above-->
```{r table_stat_soilCN, echo=F, results="asis"}
names(stattab)<-c("Statistic","Value on data","Frac. K surr >","Frac. K surr <","Frac. S surr >","Frac. S surr <")
table_nums("table_stat_soilCN",display=F)
knitr::kable(data.frame(stat=stattab),caption = "Results of non-parametric tests of tail dependence and asymmetry of tail dependence for the soil C and N dataset. Names and values on the actual C and N data are listed in the first two columns. The third (respectively, fourth) column is the fraction of Kendall-preserving surrogate datasets for which the given statistic is greater than (resp., less than) its value on the real data. The last two columns are analogous but for Spearman-preserving surrogates.")
```
